Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays

### 2021-11-29 PrevAdjSurvey.tex
CI Width Figure Captions

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_50_groups_0_005_prev}
\caption{CAPTION HERE.}
\label{fig:perfect_confidence_interval_width_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_50_groups_0_05_prev}
\caption{CAPTION HERE.}
\label{fig:perfect_confidence_interval_width_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_8000_groups_0_005_prev}
\caption{CAPTION HERE.}
\label{fig:perfect_confidence_interval_width_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_8000_groups_0_05_prev}
\caption{CAPTION HERE.}
\label{fig:perfect_confidence_interval_width_8000_groups_0_05_prev}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_005_prev}
\caption{CAPTION HERE.}
\label{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_05_prev}
\caption{CAPTION HERE.}
\label{fig:imperfect_confidence_interval_width_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_005_prev}
\caption{CAPTION HERE.}
\label{fig:imperfect_confidence_interval_width_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_05_prev}
\caption{CAPTION HERE.}
\label{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_50_groups_0_005_prev}
\caption{Confidence interval width properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:perfect_confidence_interval_width_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_50_groups_0_05_prev}
\caption{Confidence interval width properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:perfect_confidence_interval_width_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_8000_groups_0_005_prev}
\caption{Confidence interval width properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:perfect_confidence_interval_width_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_8000_groups_0_05_prev}
\caption{Confidence interval width properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:perfect_confidence_interval_width_8000_groups_0_05_prev}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_005_prev}
\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_05_prev}
\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_confidence_interval_width_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_005_prev}
\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_confidence_interval_width_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_05_prev}
\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}
\end{figure}
